\Large \includegraphics[height=\baselineskip]{title.png} \\ \vspace{0.65mm} \large \normalfont CSE 227: Computer Security - Spring 2017 \\ \textit{ University of California San Diego }

### 2017-06-14 docs/paper.tex
Add usenix, review abstract and browsers

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{url,epsfig,endnotes}
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}

@@

% Authors
\author{
{\rm Chen Lai\footnote{Author names are ordered lexicographically, by last name.}}\\
\normalfont{\texttt{chl588@ucsd.edu}}
\and
{\rm Zhongrong Jian\footnotemark[\value{footnote}]}\\
\normalfont{\texttt{zhjian@ucsd.edu}}
\and
{\rm J. Sidrach\footnotemark[\value{footnote}]}\\
\normalfont{\texttt{jsidrach@ucsd.edu}}
}

@@

\abstract{
The invention of Unicode made it possible for non-English speaking people to enter the world of Internet. However, it also open up the possibilities of malicious use of URL. Sometimes different letters from different languages can look almost the same depending on the font. This paper mainly summarize the previous relevant work and analyze the current circumstance of Internationalized Domain Name Homograph Attack on the Internet via statistical approach on the websites from Alexa top 1 million rankings. Through the analysis results we will be able to provide some insight on this subject.
}

@@

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speaking people use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential security vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN Homograph Attack.
Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

\section{Background}
TODO
- Introduction to the section, two mayor players in preventing the attack, different roles: browsers vs TLDs

This section provides some background knowledge for mechanism that defends against internationalized domain name homograph attack.
There are two mayor players preventing the attack, the browsers and TLDs, with one working on the client side to detect and alert users while the other putting down policies on domain name registerar to restrict the number of possible homographs.

\subsection{Browsers}
TODO
- Rewrite, browser by browser: chrome, firefox, edge, safari
- Significant changes in the past years?
- Not updated browsers/embedded browsers?
- Screenshot of two actual domains that look the same but are different
- Cut screenshots better

Currently, most popular browsers will show the host name in Unicode depends on the language setting to defend IDN attack.
For example, Google Chrome\endnote{\url{https://www.google.com/chrome}} will display IDN in Unicode only if all characters of the domain names belong to only one language and this language has to be the user's preferred language. Figure \ref{screenshot} shows the screenshots of the original URL of \url{www.google.com} and its homograph.

\begin{figure}[t]
  \includegraphics[width=\linewidth]{images/google}
  \includegraphics[width=\linewidth]{images/fakegoogle-punycode}
  \centering
  \caption{Google(top) and its homograph(bottom) on Chrome}
  \label{screenshot}
\end{figure}

The major browsers have their own IDN policies to defend against IDN homograph attack.
Google Chrome, starting with Chrome 51, will display Punycode if certain tests fail on the input URL.
These tests include but not limited to converting to Unicode, less than one numbering systems involved, no invisible characters, etc.

Internet Explorer\endnote{\url{https://support.microsoft.com/en-us/help/17621/internet-explorer-downloads}} displays URLs in IDN form if every component contains only characters from the languages configured in \textit{Internet Options}.

Firefox\endnote{\url{https://www.mozilla.org/en-US/firefox/new/}} uses a script mixing detection algorithm based on \textit{"Moderately Restrictive" profile of Unicode Technical Report 39} and displays Unicode when URL consists of any single script, any single script plus Latin, or it's in the white-list of other combinations.

Opera\endnote{\url{http://www.opera.com}} shows IDN only for whitelisted TLDs.

Safari\endnote{\url{https://www.apple.com/safari}} has a whitelist of scripts that do not contain confusable characters and only shows the IDN form for the whitelisted scripts.

@@

The detection of homograph domain names was done using an algorithm to check if two strings are confusable.
This algorithm is described in the \textit{Unicode Technical Standard \#39}\endnote{\url{http://www.unicode.org/reports/tr39}}.
The approach followed has some caveats, that could be addressed in future work.
For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking Unicode character.
More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top-level domains following the same procedure.
All things considered, we still think this approach is a valuable first step.

@@

@@

\begin{table*}[ht!]
\centering
\begin{tabular}{lrr}
\hline
Domains                                           & \#                         & \%                         \\ \hline
\itshape\sffamily{Canonical domain names}         & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
\hspace{0.5cm} Without canonical homograph        & 1044301                    & 2.74\%                     \\ \hline
\end{tabular}
\caption{Overview of the clustering results.}
\label{clustering-results}
\end{table*}

@@

\begin{table}[ht!]
\centering
\begin{tabular}{lr}
\hline
Domain       & \# of IDN homographs \\ \hline
google.com   & 24                   \\
youtube.com  & 3                    \\
facebook.com & 9                    \\
baidu.com    & 3                    \\
yahoo.com    & 4                    \\
reddit.com   & 1                    \\
qq.com       & 2                    \\
taobao.com   & 1                    \\
live.com     & 1                    \\
vk.com       & 6                    \\ \hline
\end{tabular}
\caption{Top ten .com domains in the Alexa ranking with IDN homographs.}
\label{top-com-alexa-with-idns}
\end{table}

@@

\begin{table}[ht!]
\centering
\begin{tabular}{lrr}
\hline
Status                               & \#                     & \%                         \\ \hline
\itshape\sffamily{Canonical}         & \itshape\sffamily{88}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} Parking               & 64                     & 6.04\%                     \\
\hspace{0.5cm} Redirect              & 24                     & 2.27\%                     \\
\itshape\sffamily{Third Party}       & \itshape\sffamily{971} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} Redirect to Canonical & 39                     & 3.68\%                     \\
\hspace{0.5cm} Unrelated             & 29                     & 2.74\%                     \\
\hspace{0.5cm} Parking               & 872                    & 82.34\%                    \\
\hspace{0.5cm} Scam                  & 31                     & 2.93\%                     \\ \hline
\end{tabular}
\caption{Breakdown of the manually classified homograph IDNs.}
\label{manually-classified-idns}
\end{table}

@@

\begin{table*}[ht!]
\centering
\begin{tabular}{llr}
\hline
Registrant organization              & Registrant email           & \# of homograph IDNs \\ \hline
Domains By Proxy, LLC                & --                         & 89                   \\
Super Privacy Service c/o Dynadot    & privacy@dynadot.com        & 23                   \\
Domain Registries Foundation         & --                         & 22                   \\
Duong Thien                          & thiendv@outlook.com        & 18                   \\
Syngenuity Limited                   & manager@syngenuity.com     & 12                   \\
Helpnet: Brand Development \& Sales  & help@strongestbrands.com   & 12                   \\
ONUNO L.L.C.                         & corucas@gmail.com          & 11                   \\
Privacy Protection Service INC d/b/a & contact@privacyprotect.org & 10                   \\
Hubertus Henz                        & hu\_h5@yahoo.de            & 9                    \\
wuyu                                 & wy65535@126.com            & 7                    \\ \hline
\end{tabular}
\caption{Top ten registrants with the most homograph IDNs.}
\label{top-registrants-homograph-idns}
\end{table*}

>>>>

\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,url,epsfig,endnotes}
\providecommand{\keywords}[1]{\textbf{\textit{Keywords:}} #1}

@@

% Authors
\author{
{\rm Chen Lai\thanks{Author names are ordered lexicographically, by last name.}}\\
\normalfont{\texttt{chl588@ucsd.edu}}
\and
{\rm Zhongrong Jian\footnotemark[1]}\\
\normalfont{\texttt{zhjian@ucsd.edu}}
\and
{\rm J. Sidrach\footnotemark[1]}\\
\normalfont{\texttt{jsidrach@ucsd.edu}}
}

@@

\abstract{
The introduction of Internationalized Domain Names made access the web easier to non-English speakers.
However, it also opened the possibility of using homograph domain names maliciously.
We analyzed the potential impact of this type of attack, commonly referred to as IDN homograph attack.
Our approach was based on clustering internationalized domain names with their counterparts in the Alexa Top 1m web sites ranking.
The results obtained indicate that there are more than a thousand (at least) IDN homographs among \textit{.com} domains.
Most of them are not being used actively, but they still posses a potential security risk as there are no guarantees they will remain inactive in the future.
}

@@

\section{Introduction}
Domain names were originally designed to only support ASCII characters.
Internationalized Domain Names (IDNs) were proposed back in December 1996 by Martin D\"{u}rst\endnote{\url{https://tools.ietf.org/html/draft-duerst-dns-i18n-00}} for the purpose of letting non-English speakers use Internet without additional restrictions.
This extension involves representing Unicode characters in ASCII using Punycode, so that they could be then rendered back into their Unicode representation.
Homograph letters (different letters whose representation is almost, if not, the same), however, present a potential security vulnerability.
For example, Cyrillic letter ``a'' can look identical to Latin letter ``a'' depending on the font.
In other languages, like Chinese, there exists many homograph letters between traditional Chinese and simplified Chinese.
Malicious attackers could then register a domain where one of the letters is actually Cyrillic but whose representation matched a Latin one.
Users could be linked to this newly registered malicious page, and they may not have any visual indication (at least without further interaction) that the page is not the one they think they are visiting.

In this paper, we analyze the potential impact of this type of attack, commonly referred to as IDN homograph attack.
Section 2 explains past and present policies of major browsers and top-level domain (TLD) registrants in an attempt to prevent the attack.
Section 3 explores relevant work in the literature related to homograph attacks.
Section 4 describes the methodology of data collection and analysis adopted in this project.
Section 5 comments the different results obtained.
Section 6 addresses the ethical concerns regarding the data collection.
Section 7 presents the conclusions obtained from this project.

\section{Background}
This section summarizes different mechanisms used to defend against internationalized domain name homograph attack.
There are two mayor players trying to prevent this kind of attack, browsers and TLDs.
Browsers, on the client side, display the non-Unicode version of the domain name based on different white-lists and restrictions.
TLDs, on the other side, have different policies on domain name registrations to try to restrict the use of homographs.
A more comprehensive study would be required for other possible attack vectors, such as email clients.

\subsection{Browsers}
\begin{figure}[t]
  \includegraphics[width=\linewidth]{images/apple}
  \includegraphics[width=\linewidth]{images/fakeapple-punycode}
  \centering
  \caption{Apple's official website (top) and its IDN homograph (bottom), as displayed on Chrome 55.}
  \label{screenshot-apple}
\end{figure}

\begin{figure}[t]
  \includegraphics[width=\linewidth]{images/google}
  \includegraphics[width=\linewidth]{images/fakegoogle-punycode}
  \centering
  \caption{Google's official website (top) and its IDN homograph (bottom), as displayed on Chrome 55.}
  \label{screenshot-google}
\end{figure}

All major browsers display the URL in Punycode instead of Unicode if certain conditions are met, to defend the user against a possible IDN homograph attack.
The specific conditions, however, are different for each browser.
Figure~\ref{screenshot-apple} shows a successful attack where the homograph domain name was not detected.
Figure~\ref{screenshot-google} show an unsuccessful attack, where the URL is displayed in Punycode.

Firefox (version 54 at the time of writing) uses a script mixing detection algorithm based on the ``Moderately Restrictive'' profile defined in the \textit{Unicode Technical Standard \#39}\endnote{\url{http://www.unicode.org/reports/tr39}}.
It displays the URL in Unicode when all characters belong to a single script, to a single script plus Latin, or to a the white-list of other combinations.
Google Chrome (version 59 at the time of writing), among other things, checks Latin-look-alike Cyrillic characters in non-IDN TLDs.
This change was introduced recently, after a proof-of-concept IDN homograph attack working on Chrome was submitted to their issue tracker\endnote{\url{https://bugs.chromium.org/p/chromium/issues/detail?id=683314}}.
Internet Explorer and Edge (version 11 and 40 at the of writing, respectively) display the URL in Unicode if every component of the URL contains only characters from the languages configured in the operating system's \textit{Internet Options}.
Safari (version 10 at the time of writing) has a white-list of scripts that do not contain confusable characters, and only shows the URL in Unicode for those white-listed scripts.

@@

The detection of homograph domain names was done using an algorithm to check if two strings are confusable.
This algorithm is described in the \textit{Unicode Technical Standard \#39}.
The approach followed has some caveats, that could be addressed in future work.
For instance, it does not detect a homograph of \texttt{www.google.com}, where the first ``.'' has been replaced by a similar looking Unicode character.
More sophisticated homographs can also be generated by using Unicode characters similar to ``/''.
It is also worth noting that only domain names from the \texttt{.com} zone were considered, but similar studies could be done to other top-level domains following the same procedure.
All things considered, we still think this approach is a valuable first step.

@@

% TODO: Align tables

\begin{table*}[]
\centering
\begin{tabular}{lrr}
\hline
Domains                                           & \#                         & \%                         \\ \hline
\itshape\sffamily{Canonical domain names}         & \itshape\sffamily{458731}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} With IDN homographs                & 825                        & 6.04\%                     \\
\hspace{0.5cm} Without IDN homographs             & 457906                     & 2.27\%                     \\
\itshape\sffamily{Internationalized Domain Names} & \itshape\sffamily{1045400} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} With canonical homograph           & 1099                       & 3.68\%                     \\
\hspace{0.5cm} Without canonical homograph        & 1044301                    & 2.74\%                     \\ \hline
\end{tabular}
\caption{Overview of the clustering results.}
\label{clustering-results}
\end{table*}

\begin{table}[]
\centering
\begin{tabular}{lr}
\hline
Domain       & \# of IDN homographs \\ \hline
google.com   & 24                   \\
youtube.com  & 3                    \\
facebook.com & 9                    \\
baidu.com    & 3                    \\
yahoo.com    & 4                    \\
reddit.com   & 1                    \\
qq.com       & 2                    \\
taobao.com   & 1                    \\
live.com     & 1                    \\
vk.com       & 6                    \\ \hline
\end{tabular}
\caption{Top ten .com domains in the Alexa ranking with IDN homographs.}
\label{top-com-alexa-with-idns}
\end{table}

\begin{table}[]
\centering
\begin{tabular}{lrr}
\hline
Status                               & \#                     & \%                         \\ \hline
\itshape\sffamily{Canonical}         & \itshape\sffamily{88}  & \itshape\sffamily{8.31\%}  \\
\hspace{0.5cm} Parking               & 64                     & 6.04\%                     \\
\hspace{0.5cm} Redirect              & 24                     & 2.27\%                     \\
\itshape\sffamily{Third Party}       & \itshape\sffamily{971} & \itshape\sffamily{91.69\%} \\
\hspace{0.5cm} Redirect to Canonical & 39                     & 3.68\%                     \\
\hspace{0.5cm} Unrelated             & 29                     & 2.74\%                     \\
\hspace{0.5cm} Parking               & 872                    & 82.34\%                    \\
\hspace{0.5cm} Scam                  & 31                     & 2.93\%                     \\ \hline
\end{tabular}
\caption{Breakdown of the manually classified homograph IDNs.}
\label{manually-classified-idns}
\end{table}

\begin{table*}[]
\centering
\begin{tabular}{llr}
\hline
Registrant organization              & Registrant email           & \# of homograph IDNs \\ \hline
Domains By Proxy, LLC                & --                         & 89                   \\
Super Privacy Service c/o Dynadot    & privacy@dynadot.com        & 23                   \\
Domain Registries Foundation         & --                         & 22                   \\
Duong Thien                          & thiendv@outlook.com        & 18                   \\
Syngenuity Limited                   & manager@syngenuity.com     & 12                   \\
Helpnet: Brand Development \& Sales  & help@strongestbrands.com   & 12                   \\
ONUNO L.L.C.                         & corucas@gmail.com          & 11                   \\
Privacy Protection Service INC d/b/a & contact@privacyprotect.org & 10                   \\
Hubertus Henz                        & hu\_h5@yahoo.de            & 9                    \\
wuyu                                 & wy65535@126.com            & 7                    \\ \hline
\end{tabular}
\caption{Top ten registrants with the most homograph IDNs.}
\label{top-registrants-homograph-idns}
\end{table*}

@@

@@

@@

@@
